Title Goes Here

### 2023-10-29 paper/main.tex
skeleton of the evaluation section

\section{Case Study Protocols}

@@

\begin{itemize}
\item \textbf{RQ1:} Is \system capable of detecting insecurity in complex, multi-round protocols?
\item \textbf{RQ2:} Is \system capable of detecting insecurity in real-world protocols?
\end{itemize}

\subsection{Experiment 1: Real-world Secure Protocols}

\subsection{Experiment 2: Random Protocols}

>>>>

\section{Case Study Protocols}
\label{sec:case-study-protocols}

@@

Our empirical evaluation demonstrates \system's ability to detect bugs in secure protocols. Our experiments are designed to answer two research questions:
%
\begin{itemize}
\item \textbf{RQ1:} Is \system capable of detecting insecurity in complex, multi-round protocols?
\item \textbf{RQ2:} Is \system capable of detecting insecurity in real-world protocols?
\end{itemize}
%
To answer RQ1, we generate \emph{random protocols} of varying sizes, and evaluate \system's ability to show they are insecure. The details appear in Section~\ref{sec:experiment-1:-random}. To answer RQ2, we evaluate \system on the case study protocols described in Section~\ref{sec:case-study-protocols}. The details appear in Section~\ref{sec:experiment-2:-real}. In both cases, \system is able to detect insecurity in the target protocols in under a minute.

\subsection{Experiment 1: Random Protocols}
\label{sec:experiment-1:-random}

\paragraph{Experiment setup.}

\paragraph{Results.}

\subsection{Experiment 2: Real-world Protocols}
\label{sec:experiment-2:-real}

\paragraph{Experiment setup.}

\paragraph{Results.}
